HyperLogLog: Exponentially Bad in Adversarial Settings

### 2021-01-13 docs/HLL_exp_bad/rebuttal.txt

Weaknesses
----------
The empirical results described in Section 6, while promising, are not necessarily something a real-world attacker could meaningfully use (the set of 4-character ASCII strings, or a set of 250K random strings). Similarly, a real-world attacker is unlikely to be lucky enough to get to attack a target with no honest inputs already in the sketch. Those model scenarios might or might not faithfully model a real attack like suggested in section 3 (e.g. a port scanner that evades detection).

Comments for author
-------------------
It entirely depends on your audience, but as an industry schlub I find pseudocode notation easier to understand than mathematical notation. I understand the good reasons for using math notation. I'll be excited to see the source code when you can release it!

I would love to see future work that operationalizes the attack. For example, a modification to ZMap or nmap that successfully evades detection against a defender using Redis for log analysis would be an excellent paper to present at USENIX WOOT or another similar conference.

Requested Changes
-----------------
No significant changes.

Missing reference in Section 5: "In S4, the analysis is the same as in Section ."

Probable typo in Section 6: "only, thus that are initially empty." Probably should be "thus they are".
